Results_paper1

### 2019-04-15 Paper1_results.Rmd
Fixed

# Loading the data
load("Data_P1/MODIS_Chloro.RData") # Extracted chlorophyll data
load("Data_P1/site_list_sub.Rdata") # Site list of all the sites along the west coast

@@

## Upwelling indeces

>>>>

# Loading the data
load("Data_P1/MODIS_Chloro.RData") # Extracted/Raw chlorophyll data
load("Data_P1/site_list_sub.Rdata") # Site list of all the sites along the west coast

@@

## EOF's
